### 2023-10-25 results/airline.tex
Changed to subsec
All afternoon work

\subsubsection{Network configuration}

@@

\begin{figure}[H]
  \centering
  \begin{tikztimingtable}%TODO change or find other way
    $e_0$       & x 2H 6L     L 2H 6L     L L x\\
    $e_1$       & x 2L 2H 4L  L 2L 2H 4L  L L x\\
    $e_2$       & x 4L 2H 2L  L 4L 2H 2L  L L x\\
    $e_3$       & x 6L 2H     L 6L 2H     L L x\\
    $e_{next}$  & x 8L        H 8L        H L x\\
    $e_{in}$    & x 8H        L 8H        L L x\\
    $e_{out}$   & x 8L        L 8L        L H x\\
    \extracode
    \tablerules
    \begin{pgfonlayer}{background}
      %\vertlines[help lines]{0.55,10.55}
      %\vertlines[red]{1.6,5.6,15.6}
      %\vertlines[blue]{3.6,9.6,15.6}
    \end{pgfonlayer}
  \end{tikztimingtable}
  \caption{Flags time diagram for the airline problem with $n_s=4$}
  \label{tim:airline}
\end{figure}

@@

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    \cellcolor[HTML]{808080}\acs{RMSE} & Target data & \specialcell{Digital prediction with\\default activation functions} & \specialcell{Digital prediction with\\analog activation functions}\\
    \hline
    Target data &\cellcolor[HTML]{202020} & $54.60$ & $52.27$\\
    \hline
    \specialcell{Digital prediction with\\default activation functions}  & $54.60$ & \cellcolor[HTML]{202020} & $78.64$\\
    \hline
    \specialcell{Digital prediction with\\analog activation functions} & $52.27$ & $78.64$ & \cellcolor[HTML]{202020}\\
    \hline
  \end{tabular}
  \caption{\acp{RMSE} of each curve to the others}
  \label{tab:airlineDigital}
\end{table}

Both predictions have similar \ac{RMSE} to the target curve. They have a \ac{RMSE} of $54.60$ for the \ac{LSTM} using the default activation functions (sigmoid and \ac{tanh} functions) and $52.27$ for the one using the analog activation functions (\cref{sec:af}). The error difference is so low (about two thousands passengers) that the difference may just come from the training and the initial values of the weights. They both approach the target curve pretty well. These error could be lowered by training for more epochs. This is not done because it diverges too much from the focus of the thesis.

The two predictions are very different from each other, the error rate between the two is of $78.64$, which is significantly higher than the \ac{RMSE} of the curves to the target curve.

@@

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    \multirow{2}{*}{\acs{RMSE}} & \multicolumn{3}{|c|}{Analog prediction}\\
    \cline{2-4}
    & $n_s=1$ & $n_s=2$ & $n_s=4$ \\
    \hline
    \specialcell{Digital prediction with\\default activation functions} & $140.68$ & $143.66$ & $139.71$\\
    \hline
  \end{tabular}
  \caption{\acp{RMSE} of each analog prediction to their associated digital prediction}
  \label{tab:airlineAnalogNoC}
\end{table}

@@

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    \multirow{2}{*}{\acs{RMSE}} & \multicolumn{3}{|c|}{Analog prediction}\\
    \cline{2-4}
    & $n_s=1$ & $n_s=2$ & $n_s=4$ \\
    \hline
    \specialcell{Digital prediction with\\analog activation functions} & $28.41$ & $92.57$ & $68.51$\\
    \hline
  \end{tabular}
  \caption{\acp{RMSE} of each analog prediction to their associated digital prediction}
  \label{tab:airlineAnalog}
\end{table}

@@

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    \multicolumn{2}{|c}{\multirow{2}{*}{\ac{RMSE}}} & \multicolumn{3}{|c|}{Analog prediction}\\
    \cline{3-5}
    \multicolumn{2}{|c}{} & \multicolumn{1}{|c|}{$n_s=1$} & $n_s=2$ & $n_s=4$ \\
    \hline
    \multirow{3}{*}{Analog prediction} & $n_s=1$ &\cellcolor[HTML]{202020} & $64.61$ & $40.63$\\
    \cline{2-5}
    & $n_s=2$  & $64.61$ & \cellcolor[HTML]{202020} & $25.75$\\
    \cline{2-5}
    & $n_s=4$ & $40.63$ & $25.75$ & \cellcolor[HTML]{202020}\\
    \hline
  \end{tabular}
  \caption{\acp{RMSE} of each analog prediction to the others depending on the serial size ($n_s$)}
  \label{tab:airlineAnalogError}
\end{table}

>>>>

\subsection{Network configuration}

@@

\begin{figure}[H]
  \centering
  \begin{tikztimingtable}%TODO change or find other way
    $e_0$       & x 2H 6L     L 2H 6L     L L x\\
    $e_1$       & x 2L 2H 4L  L 2L 2H 4L  L L x\\
    $e_2$       & x 4L 2H 2L  L 4L 2H 2L  L L x\\
    $e_3$       & x 6L 2H     L 6L 2H     L L x\\
    $e_{next}$  & x 8L        H 8L        H L x\\
    $e_{in}$    & x 8H        L 8H        L L x\\
    $e_{out}$   & x 8L        L 8L        L H x\\
    \extracode
    \tablerules
    \begin{pgfonlayer}{background}
      \vertlines[help lines]{0.55,8.55,9.55,17.55,18.55}
      %\vertlines[red]{1.6,5.6,15.6}
      %\vertlines[blue]{3.6,9.6,15.6}
    \end{pgfonlayer}
  \end{tikztimingtable}
  \caption{Flags time diagram for the airline problem with $n_s=4$}
  \label{tim:airline}
\end{figure}

@@

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    \cellcolor[HTML]{808080}\acs{RMSE} & Target data & \specialcell{Digital prediction with\\default activation functions} & \specialcell{Digital prediction with\\analog activation functions}\\
    \hline
    Target data &\cellcolor[HTML]{202020} & $54.6$ & $52.3$\\
    \hline
    \specialcell{Digital prediction with\\default activation functions}  & $54.6$ & \cellcolor[HTML]{202020} & $78.6$\\
    \hline
    \specialcell{Digital prediction with\\analog activation functions} & $52.3$ & $78.6$ & \cellcolor[HTML]{202020}\\
    \hline
  \end{tabular}
  \caption{\acp{RMSE} of each curve to the others}
  \label{tab:airlineDigital}
\end{table}

Both predictions have similar \ac{RMSE} to the target curve. They have a \ac{RMSE} of $54.6$ for the \ac{LSTM} using the default activation functions (sigmoid and \ac{tanh} functions) and $52.3$ for the one using the analog activation functions (\cref{sec:af}). The error difference is so low (about two thousands passengers) that the difference may just come from the training and the initial values of the weights. They both approach the target curve pretty well. These error could be lowered by training for more epochs. This is not done because it diverges too much from the focus of the thesis.

The two predictions are very different from each other, the error rate between the two is of $78.6$, which is significantly higher than the \ac{RMSE} of the curves to the target curve.

@@

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    \multirow{2}{*}{\acs{RMSE}} & \multicolumn{3}{|c|}{Analog prediction}\\
    \cline{2-4}
    & $n_s=1$ & $n_s=2$ & $n_s=4$ \\
    \hline
    \specialcell{Digital prediction with\\default activation functions} & $141$ & $144$ & $140$\\
    \hline
  \end{tabular}
  \caption{\acp{RMSE} of each analog prediction to their associated digital prediction}
  \label{tab:airlineAnalogNoC}
\end{table}

@@

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    \multirow{2}{*}{\acs{RMSE}} & \multicolumn{3}{|c|}{Analog prediction}\\
    \cline{2-4}
    & $n_s=1$ & $n_s=2$ & $n_s=4$ \\
    \hline
    \specialcell{Digital prediction with\\analog activation functions} & $28.4$ & $92.6$ & $68.5$\\
    \hline
  \end{tabular}
  \caption{\acp{RMSE} of each analog prediction to their associated digital prediction}
  \label{tab:airlineAnalog}
\end{table}

@@

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    \multicolumn{2}{|c}{\multirow{2}{*}{\ac{RMSE}}} & \multicolumn{3}{|c|}{Analog prediction}\\
    \cline{3-5}
    \multicolumn{2}{|c}{} & \multicolumn{1}{|c|}{$n_s=1$} & $n_s=2$ & $n_s=4$ \\
    \hline
    \multirow{3}{*}{Analog prediction} & $n_s=1$ &\cellcolor[HTML]{202020} & $64.6$ & $40.6$\\
    \cline{2-5}
    & $n_s=2$  & $64.6$ & \cellcolor[HTML]{202020} & $25.8$\\
    \cline{2-5}
    & $n_s=4$ & $40.6$ & $25.8$ & \cellcolor[HTML]{202020}\\
    \hline
  \end{tabular}
  \caption{\acp{RMSE} of each analog prediction to the others depending on the serial size ($n_s$)}
  \label{tab:airlineAnalogError}
\end{table}

### 2023-10-25 results/celegans.tex
All afternoon work

The digital results of the \ac{C. elegans} dataset are quite numerous, not all of them can be displayed and analyzed. For this reason, only a selected four sequences will be displayed as the results of the dataset are not the focus of this thesis. The full work around the \ac{C. elegans} dataset and problem is done in \cite{celegans}.

\begin{figure}[H]
  \centering
  \begin{minipage}{\columnwidth}
    \subfloat[Analog prediction for the DB1 neuron\label{graph:digital5BD1Celegans}]{\includesvg[width=0.5\textwidth, pretex=\tiny]{results/celegans/digital5DB1}}%
    \hfill
    \subfloat[Analog prediction for the LUAL neuron\label{graph:digital5LUALCelegans}]{\includesvg[width=0.5\textwidth,pretex=\tiny]{results/celegans/digital5LUAL}}%
  \end{minipage}
  \begin{minipage}{\columnwidth}
    \subfloat[Analog prediction for the PVR neuron\label{graph:digital5PVRCelegans}]{\includesvg[width=0.5\textwidth, pretex=\tiny]{results/celegans/digital5PVR}}%
    \hfill
    \subfloat[Analog prediction for the VB1 neuron\label{graph:digital5VB1Celegans}]{\includesvg[width=0.5\textwidth,pretex=\tiny]{results/celegans/digital5VB1}}%
  \end{minipage}
  \caption{\ac{C. elegans} digital responses with their digital counterparts spread out for each output neuron}
  \label{graph:spread5Celegans}
\end{figure}

The results will be analyzed by focusing on a single data sequence, the training data sequence available in \cref{graph:io5Celegans}.

\subsection{Analog results}
\label{subsec:analogCelegans}

@@

A big problem that is immediatly visible is that the LUAL output neuron's analogly predicted response is negative when it should not be. For an unknown reason the analog results of the LUAL neuron seem to be negative instead of positive. This is the case for the analog response to all sequences. This issue most likely comes from dense layer that comes after the \ac{LSTM}. In order to keep using the data the output of this neuron will be flipped over the x-axis.

@@

The smoothed out and exploitable analog predictions are available in \cref{graph:smooth5Celegans}. Theses graphs allow for a much easier visualisation of the results.

The best looking output of the four predicted neurons responses is the one from PVR. That is confirmed by its error rate to the digital prediction. It is the lowest of the four, however, it isn't close enough to the digital prediction.

All four analog predictions are very close to each others

\begin{figure}[H]
  \centering
  \begin{minipage}{\columnwidth}
    \subfloat[Averaged analog prediction for the DB1 neuron\label{graph:smooth5BD1Celegans}]{\includesvg[width=0.5\textwidth, pretex=\tiny]{results/celegans/smooth5DB1}}%
    \hfill
    \subfloat[Averaged analog prediction for the LUAL neuron\label{graph:smooth5LUALCelegans}]{\includesvg[width=0.5\textwidth,pretex=\tiny]{results/celegans/smooth5LUAL}}%
  \end{minipage}
  \begin{minipage}{\columnwidth}
    \subfloat[Averaged analog prediction for the PVR neuron\label{graph:smooth5PVRCelegans}]{\includesvg[width=0.5\textwidth, pretex=\tiny]{results/celegans/smooth5PVR}}%
    \hfill
    \subfloat[Averaged analog prediction for the VB1 neuron\label{graph:smooth5VB1Celegans}]{\includesvg[width=0.5\textwidth,pretex=\tiny]{results/celegans/smooth5VB1}}%
  \end{minipage}
  \caption{\ac{C. elegans} smoothed out analog responses averaged with $21$ neighbors, spread out for each output neuron}
  \label{graph:smooth5Celegans}
\end{figure}

>>>>

The results will be analyzed by focusing on two data sequence, the first being simple inputs expecting simple outputs and the second being more complex, those sequences are the ones in \cref{graph:io5Celegans,graph:io15Celegans}. We'll identify those as sequence 5 and sequence 15 respectively.

The digital results of the \ac{C. elegans} dataset are quite numerous, not all of them can be displayed and analyzed. For this reason, only the two previously selected sequences will be displayed as the results of the dataset are not the focus of this thesis. The full work concerning the \ac{C. elegans} dataset and problem is done in \cite{celegans}.

\begin{figure}[H]
  \centering
  \begin{minipage}{\columnwidth}
    \subfloat[Analog prediction for the DB1 neuron\label{graph:digital5BD1Celegans}]{\includesvg[width=0.5\textwidth, pretex=\tiny]{results/celegans/digital5DB1}}%
    \hfill
    \subfloat[Analog prediction for the LUAL neuron\label{graph:digital5LUALCelegans}]{\includesvg[width=0.5\textwidth,pretex=\tiny]{results/celegans/digital5LUAL}}%
  \end{minipage}
  \begin{minipage}{\columnwidth}
    \subfloat[Analog prediction for the PVR neuron\label{graph:digital5PVRCelegans}]{\includesvg[width=0.5\textwidth, pretex=\tiny]{results/celegans/digital5PVR}}%
    \hfill
    \subfloat[Analog prediction for the VB1 neuron\label{graph:digital5VB1Celegans}]{\includesvg[width=0.5\textwidth,pretex=\tiny]{results/celegans/digital5VB1}}%
  \end{minipage}
  \caption{\ac{C. elegans} digital responses spread out for each output neuron}
  \label{graph:digital5Celegans}
\end{figure}

\Cref{graph:digital5Celegans,graph:digital15Celegans} are the digital predictions of the selected dat sequences. They all show a decent results, their \ac{RMSE} can be found at \cref{tab:celegansDigital}.

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    \cellcolor[HTML]{808080}\acs{RMSE} & BD1 & LUAL & PVR & VB1\\
    \hline
    Sequence 5 & $5.02\cdot 10^{-2}$ & $1.68\cdot 10^{-1}$ & $1.32\cdot 10^{-1}$ & $5.07\cdot 10^{-2}$\\
    \hline
    Sequence 15 & $6.98\cdot 10^{-2}$ & $1.39\cdot 10^{-1}$ & $1.86\cdot 10^{-1}$ & $6.63\cdot 10^{-2}$\\
    \hline
  \end{tabular}
  \caption{\acp{RMSE} of each neuron's prediction for the two selected sequences}
  \label{tab:celegansDigital}
\end{table}

A pattern can be observed here, the error rates are lower for the DB1 and VB1 neurons.

\begin{figure}[H]
  \centering
  \begin{minipage}{\columnwidth}
    \subfloat[Analog prediction for the DB1 neuron\label{graph:digital15BD1Celegans}]{\includesvg[width=0.5\textwidth, pretex=\tiny]{results/celegans/digital15DB1}}%
    \hfill
    \subfloat[Analog prediction for the LUAL neuron\label{graph:digital15LUALCelegans}]{\includesvg[width=0.5\textwidth,pretex=\tiny]{results/celegans/digital15LUAL}}%
  \end{minipage}
  \begin{minipage}{\columnwidth}
    \subfloat[Analog prediction for the PVR neuron\label{graph:digital15PVRCelegans}]{\includesvg[width=0.5\textwidth, pretex=\tiny]{results/celegans/digital15PVR}}%
    \hfill
    \subfloat[Analog prediction for the VB1 neuron\label{graph:digital15VB1Celegans}]{\includesvg[width=0.5\textwidth,pretex=\tiny]{results/celegans/digital15VB1}}%
  \end{minipage}
  \caption{\ac{C. elegans} digital responses spread out for each output neuron}
  \label{graph:digital15Celegans}
\end{figure}

\subsection{Analog results of sequence 5}
\label{subsec:analog5Celegans}

@@

All curves seem to all have a similar issue, the signal is late to go up. However, the reason for this behavior is still unknown. This can be adjusted manually in the graph until the reason for this issue is found.

@@

The adjusted (smoothed out and slided to the left to match the digital prediction best) and exploitable analog predictions are available in \cref{graph:smooth5Celegans}. Theses graphs allow for a much easier and better visualisation of the results.

\begin{figure}[H]
  \centering
  \includesvg[width=\linewidth]{results/celegans/rmse5}
  \caption{\acp{RMSE} of each neuron's analog prediction and adjusted analog prediction for sequence 5}
  \label{bar:rmse5}
\end{figure}

The \cref{bar:rmse5} shows that adjusted or not, the errors are in the expected range. Adjusting the results reduces the error a bit, mainly due to the sliding of the results. Smoothing out the curve doesn't affect the error as it simply does a local average of each value. The erros are, once again higher when obtained with the analog simulation than with the digital inference.

\begin{figure}[H]
  \centering
  \begin{minipage}{\columnwidth}
    \subfloat[Averaged analog prediction for the DB1 neuron\label{graph:smooth5BD1Celegans}]{\includesvg[width=0.5\textwidth, pretex=\tiny]{results/celegans/smooth5DB1}}%
    \hfill
    \subfloat[Averaged analog prediction for the LUAL neuron\label{graph:smooth5LUALCelegans}]{\includesvg[width=0.5\textwidth,pretex=\tiny]{results/celegans/smooth5LUAL}}%
  \end{minipage}
  \begin{minipage}{\columnwidth}
    \subfloat[Averaged analog prediction for the PVR neuron\label{graph:smooth5PVRCelegans}]{\includesvg[width=0.5\textwidth, pretex=\tiny]{results/celegans/smooth5PVR}}%
    \hfill
    \subfloat[Averaged analog prediction for the VB1 neuron\label{graph:smooth5VB1Celegans}]{\includesvg[width=0.5\textwidth,pretex=\tiny]{results/celegans/smooth5VB1}}%
  \end{minipage}
  \caption{\ac{C. elegans} smoothed out and slided analog responses averaged with $21$ neighbors, spread out for each output neuron}
  \label{graph:smooth5Celegans}
\end{figure}

\subsection{Analog results of sequence 15}
\label{subsec:analog15Celegans}

\begin{figure}[H]
  \centering
  \includesvg[width=\linewidth]{results/celegans/out15}
  \caption{\acs{C. elegans} analog responses with their digital counterparts}
  \label{graph:celegansAnalog0}
\end{figure}

The response have thus been sperated into four graphs. One for every neuron for better readability. The target response was also added to all four graphs to highlight the objective of the \ac{NN}. Those graphs can be found in \cref{graph:spread15Celegans}.

All curves seem to all have a similar issue, the signal is late to go up. However, the reason for this behavior is still unknown. This can be adjusted manually in the graph until the reason for this issue is found.

\begin{figure}[H]
  \centering
  \begin{minipage}{\columnwidth}
    \subfloat[Analog prediction for the DB1 neuron\label{graph:out15BD1Celegans}]{\includesvg[width=0.5\textwidth, pretex=\tiny]{results/celegans/out15DB1}}%
    \hfill
    \subfloat[Analog prediction for the LUAL neuron\label{graph:out15LUALCelegans}]{\includesvg[width=0.5\textwidth,pretex=\tiny]{results/celegans/out15LUAL}}%
  \end{minipage}
  \begin{minipage}{\columnwidth}
    \subfloat[Analog prediction for the PVR neuron\label{graph:out15PVRCelegans}]{\includesvg[width=0.5\textwidth, pretex=\tiny]{results/celegans/out15PVR}}%
    \hfill
    \subfloat[Analog prediction for the VB1 neuron\label{graph:out15VB1Celegans}]{\includesvg[width=0.5\textwidth,pretex=\tiny]{results/celegans/out15VB1}}%
  \end{minipage}
  \caption{\ac{C. elegans} analog responses with their digital counterparts spread out for each output neuron}
  \label{graph:spread15Celegans}
\end{figure}

\begin{figure}[H]
  \centering
  \includesvg[width=\linewidth]{results/celegans/rmse15}
  \caption{\acp{RMSE} of each neuron's analog prediction and adjusted analog prediction for sequence 15}
  \label{bar:rmse15}
\end{figure}

The \cref{bar:rmse15} shows that adjusted or not, the errors are in the expected range. The PVR output neuron seems to be hardest to reproduce during this sequence as its error is much greater than for the others.

\begin{figure}[H]
  \centering
  \begin{minipage}{\columnwidth}
    \subfloat[Averaged analog prediction for the DB1 neuron\label{graph:smooth15BD1Celegans}]{\includesvg[width=0.5\textwidth, pretex=\tiny]{results/celegans/smooth15DB1}}%
    \hfill
    \subfloat[Averaged analog prediction for the LUAL neuron\label{graph:smooth15LUALCelegans}]{\includesvg[width=0.5\textwidth,pretex=\tiny]{results/celegans/smooth15LUAL}}%
  \end{minipage}
  \begin{minipage}{\columnwidth}
    \subfloat[Averaged analog prediction for the PVR neuron\label{graph:smooth15PVRCelegans}]{\includesvg[width=0.5\textwidth, pretex=\tiny]{results/celegans/smooth15PVR}}%
    \hfill
    \subfloat[Averaged analog prediction for the VB1 neuron\label{graph:smooth15VB1Celegans}]{\includesvg[width=0.5\textwidth,pretex=\tiny]{results/celegans/smooth15VB1}}%
  \end{minipage}
  \caption{\ac{C. elegans} smoothed out and slided analog responses averaged with $21$ neighbors, spread out for each output neuron}
  \label{graph:smooth15Celegans}
\end{figure}

The results are a bit worse for this second sequence. That was expected as the inputs and the expected outputs are far more complex.
